\Title

### 2021-06-04 manuscript/content.tex
Small changes to manuscript, improve format of RMS scores

Figure \ref{fig:eql-boost-airborne}a shows the difference between the target
grid and the predictions made by the gradient-boosted equivalent sources.
Figure \ref{fig:eql-boost-airborne}b shows the RMS error of the
residuals after each iteration, exposing how the gradient-boosting algorithm
converges to a minimum fitting error.

>>>>

Figure \ref{fig:eql-boost-airborne}a shows the differences between the target
grid and the predictions made by the gradient-boosted equivalent sources.
Figure \ref{fig:eql-boost-airborne}b shows the RMS error of the
residuals after each iteration, exposing how the gradient-boosting algorithm
converges to a minimum fitting error.

Worth noting that the RMS error achieved by the gradient-boosted equivalent
sources is comparable to the values obtained by the regular equivalent sources
in Section \ref{sec:synthetic_distributions}.
